### 2020-02-06 presentations/jsps_2020-03-01/index.Rmd
Use PNG for species dist maps, much faster to load

# Define function for making species ranking table
make_species_ranking_table <- function (ranking_data, motif_select, taxon_select = NULL, slice_n = 10) {

  ranking_data_sliced <- ranking_data %>%
    filter(motif == motif_select) %>%
    # Select top-scoring species with high SD
    # (high SD should indicate mostly contributing to
    # a single motif)
    arrange(desc(score), desc(score_sd)) %>%
    slice(1:slice_n) %>%
    select(taxon, score) %>%
    mutate(score = as.factor(score)) %>%
    # Arrange alphabetically within score
    arrange(desc(score), taxon)

@@

  if(!is.null(taxon_select))
    table <-
      table %>%
      tab_style(
        style = list(
          cell_fill(
            color = "red",
            alpha = 1.0
          )
        ),
        locations = cells_data(
          columns = everything(),
          rows = taxon == ranking_data_sliced$taxon[[taxon_select]])
      )

@@

# Define function to make simple distribution map for a species
plot_distribution <- function (ranking_data, motif_select, taxon_select, occ_data, show_title = TRUE) {

   ranking_data <- ranking_data %>%
    filter(motif == motif_select) %>%
    arrange(desc(score), desc(score_sd)) %>%
    select(taxon, score) %>%
    mutate(score = as.factor(score)) %>%
    arrange(desc(score), taxon)

  cells_present <-
    occ_data %>%
    filter(taxon_name == ranking_data$taxon[[taxon_select]]) %>%
    select(secondary_grid_code) %>%
    unique %>%
    mutate(present = TRUE)

@@

  if(isTRUE(show_title))
    plot <- plot +
    labs(
      title = ranking_data$taxon[[taxon_select]]
    )

@@

```{r write_out_motif_maps, eval = FALSE}
# Don't run when making slides, but it's a useful practice to check the
# distributions for the top 10 taxa for each motif
plot_dist_by_motif <- function(species_ranking, motif, occ_data_ferns) {
  dist_maps <- purrr::map(1:10, ~plot_distribution(species_ranking, motif, ., occ_data_ferns)) %>%
    patchwork::wrap_plots(ncol = 2, nrow = 5)

@@

.pull-right-narrow[
```{r ecos-motif-1-focus-3}
make_species_ranking_table(species_ranking, 1, 3)
plot_distribution(species_ranking, 1, 3, occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-1-focus-7}
make_species_ranking_table(species_ranking, 1, 7)
plot_distribution(species_ranking, 1, 7, occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-2-focus-1}
make_species_ranking_table(species_ranking, 2, 1)
plot_distribution(species_ranking, 2, 1, occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-2-focus-2}
make_species_ranking_table(species_ranking, 2, 2)
plot_distribution(species_ranking, 2, 2, occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-3-focus-3}
make_species_ranking_table(species_ranking, 3, 3)
plot_distribution(species_ranking, 3, 3, occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-3-focus-7}
make_species_ranking_table(species_ranking, 3, 7)
plot_distribution(species_ranking, 3, 7, occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-4-focus-2}
make_species_ranking_table(species_ranking, 4, 2)
plot_distribution(species_ranking, 4, 2, occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-4-focus-8}
make_species_ranking_table(species_ranking, 4, 8)
plot_distribution(species_ranking, 4, 8, occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-5-focus-3}
make_species_ranking_table(species_ranking, 5, 3)
plot_distribution(species_ranking, 5, 3, occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-5-focus-7}
make_species_ranking_table(species_ranking, 5, 7)
plot_distribution(species_ranking, 5, 7, occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-6}
make_species_ranking_table(species_ranking, 6)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-6-focus-1}
make_species_ranking_table(species_ranking, 6, 1)
plot_distribution(species_ranking, 6, 1, occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-6-focus-2}
make_species_ranking_table(species_ranking, 6, 2)
plot_distribution(species_ranking, 6, 2, occ_data_ferns, show_title = FALSE)
```
]

>>>>

# Define function for making species ranking table
make_species_ranking_table <- function (ranking_data, motif_select, taxon_select = NULL, taxon_include = "", slice_n = 10) {

  ranking_data_sliced <- ranking_data %>%
    filter(motif == motif_select) %>%
    mutate(include = ifelse(taxon %in% taxon_include, 1, 0)) %>%
    # Select top-scoring species with high SD
    # (high SD should indicate mostly contributing to
    # a single motif)
    arrange(desc(include), desc(score), desc(score_sd)) %>%
    slice(1:slice_n) %>%
    select(taxon, score) %>%
    mutate(score = as.factor(score)) %>%
    # Arrange alphabetically within score
    arrange(desc(score), taxon)

  if(is.numeric(taxon_select)) taxon_select <- ranking_data_sliced$taxon[[taxon_select]]

@@

  if(!is.null(taxon_select))
    table <-
      table %>%
      tab_style(
        style = list(
          cell_fill(
            color = "red",
            alpha = 1.0
          )
        ),
        locations = cells_data(
          columns = everything(),
          rows = taxon == taxon_select)
      )

@@

# Define function to make simple distribution map for a species
plot_distribution <- function (ranking_data, motif_select, taxon_select, occ_data, show_title = FALSE, taxon_include = "") {

   ranking_data <- ranking_data %>%
    filter(motif == motif_select) %>%
    mutate(include = ifelse(taxon %in% taxon_include, 1, 0)) %>%
    arrange(desc(include), desc(score), desc(score_sd)) %>%
    select(taxon, score) %>%
    mutate(score = as.factor(score)) %>%
    arrange(desc(score), taxon)

  if(is.numeric(taxon_select)) taxon_select <- ranking_data$taxon[[taxon_select]]

  cells_present <-
    occ_data %>%
    filter(taxon_name == taxon_select) %>%
    select(secondary_grid_code) %>%
    unique %>%
    mutate(present = TRUE)

@@

  if(isTRUE(show_title))
    plot <- plot +
    labs(
      title = taxon_select
    )

@@

```{r write_out_motif_maps, eval = FALSE}
# Don't run when making slides, but it's a useful practice to check the
# distributions for the top 10 taxa for each motif
plot_dist_by_motif <- function(species_ranking, motif, occ_data_ferns) {
  dist_maps <- purrr::map(1:10, ~plot_distribution(species_ranking, motif, ., occ_data_ferns, show_title = TRUE)) %>%
    patchwork::wrap_plots(ncol = 2, nrow = 5)

@@

.pull-right-narrow[
```{r ecos-motif-1-focus-3, dev = "png"}
make_species_ranking_table(species_ranking, 1, "Equisetum arvense")
plot_distribution(species_ranking, 1, "Equisetum arvense", occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-1-focus-7, dev = "png"}
make_species_ranking_table(species_ranking, 1, "Athyrium vidalii")
plot_distribution(species_ranking, 1, "Athyrium vidalii", occ_data_ferns)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-2-focus-1, dev = "png"}
make_species_ranking_table(species_ranking, 2, "Adiantum pedatum")
plot_distribution(species_ranking, 2, "Adiantum pedatum", occ_data_ferns)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-2-focus-2, dev = "png"}
make_species_ranking_table(species_ranking, 2, "Arachniodes borealis")
plot_distribution(species_ranking, 2, "Arachniodes borealis", occ_data_ferns)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-3-focus-3, dev = "png"}
make_species_ranking_table(species_ranking, 3, "Dryopteris erythrosora")
plot_distribution(species_ranking, 3, "Dryopteris erythrosora", occ_data_ferns)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-3-focus-7, dev = "png"}
make_species_ranking_table(species_ranking, 3, "Odontosoria chinensis")
plot_distribution(species_ranking, 3, "Odontosoria chinensis", occ_data_ferns)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-4-focus-2, dev = "png"}
make_species_ranking_table(species_ranking, 4, "Blechnum niponicum")
plot_distribution(species_ranking, 4, "Blechnum niponicum", occ_data_ferns)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-4-focus-8, dev = "png"}
make_species_ranking_table(species_ranking, 4, "Polystichum retrosopaleaceum")
plot_distribution(species_ranking, 4, "Polystichum retrosopaleaceum", occ_data_ferns)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-5-focus-3, dev = "png"}
make_species_ranking_table(species_ranking, 5, "Dicranopteris linearis")
plot_distribution(species_ranking, 5, "Dicranopteris linearis", occ_data_ferns)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-5-focus-7, dev = "png"}
make_species_ranking_table(species_ranking, 5, "Polystichum tagawanum")
plot_distribution(species_ranking, 5, "Polystichum tagawanum", occ_data_ferns, show_title = FALSE)
```
]

@@

.pull-right-narrow[
```{r ecos-motif-6}
make_species_ranking_table(species_ranking, 6, taxon_include = c("Angiopteris lygodiifolia", "Ctenitis subglandulosa"))
```
]

@@

.pull-right-narrow[
```{r ecos-motif-6-focus-2, dev = "png"}
make_species_ranking_table(species_ranking, 6, "Angiopteris lygodiifolia", taxon_include = c("Angiopteris lygodiifolia", "Ctenitis subglandulosa"))
plot_distribution(species_ranking, 6, "Angiopteris lygodiifolia", occ_data_ferns, taxon_include = "Angiopteris lygodiifolia")
```
]

@@

.pull-right-narrow[
```{r ecos-motif-6-focus-1, dev = "png"}
make_species_ranking_table(species_ranking, 6, "Arachniodes sporadosora", taxon_include = c("Angiopteris lygodiifolia", "Ctenitis subglandulosa"))
plot_distribution(species_ranking, 6, "Arachniodes sporadosora", occ_data_ferns)
```
]
